---
title: "germination experiment"
author: "Timothée Darbois"
date: "2024-05-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(readxl)
library(germinationmetrics)
library(multcomp)
library(performance)
library(cowplot)
library(sjPlot)
library(conflicted)
library(DHARMa)
library(actuaRE)
library(ggeffects)
# conflict_prefer_all(lmerTest, quiet = TRUE) doesn't work
# conflict_prefer_all(dplyr, quiet = TRUE) same
```
function: 
```{r}
logistic_func=function(x){
  return ( exp(x) * ( 1 + exp(x) ) )
}
```


```{r}
df_Ingrid_germ <- read.csv("D:/mes_documents/M1/stage/data/csv/Copie de RangeX germination+viability (odd) - Ark 1.csv", dec = ",", na.strings = c("#DIV/0!"))
df_Ingrid_germ[, "Total.germinated"] <- NULL
df_Ingrid_germ[, "Germination.rate.in.percentage"] <- NULL
```

data timothée

delete initial_nb_seeds_1 = NA
delete batch=2 : uncomplete

```{r}
df_tim_germ<- read.csv("D:/mes_documents/M1/stage/data/csv/Copie de RangeX even number germination experiment - Feuille 1.csv", dec = ",", na.strings = c("#DIV/0!"))
df_tim_germ<-df_tim_germ[which(!is.na(df_tim_germ["Number.of.seeds.for.germination"])),]
df_tim_germ<-df_tim_germ[which((df_tim_germ["Batch"]==1)),]
df_tim_germ$Day.1 <- NULL # didn't do measurement this day


```



```{r}
df_germination <- df_Ingrid_germ # add my data afterwords

df_germination <- df_germination %>%
  mutate(nb_replicate = sub("^$", "1", gsub("\\D+", "", str_sub(df_germination$positionID, 3, 5)))) # add a column with the replicate ID ( 1 to 3)
df_germination <- df_germination %>%
  mutate(
    condi = paste(df_germination$site, df_germination$plotID, sep = " "),
    positionID_clean = str_sub(df_germination$positionID, , 2) # withdraw the number of the replicate that is written in the same column
  )

```

merging Ingrid and my df : to continue

```{r}
col_df_germ=c("site","species","treat1","treat2","blockID","plotID","positionID_clean","nb_replicate","Number.of.seeds.for.germination","Day.0","Day.2","Day.4","Day.6","Day.8","Day.12","Day.16","Day.24","Day.32","Viability.test..number.tested","Viable.seeds")

df_germination<-rbind(df_germination[col_df_germ] , df_tim_germ[col_df_germ])
```


```{r}
df_germination<-df_germination[df_germination$species %in% c("CN","SP","TP","PS","PL","LM","LV","CC"), ]

df_germination <- df_germination %>%
  mutate(merge_ID = paste(site, blockID, plotID, positionID_clean, sep = " "))

df_germination <- df_germination %>%
  mutate(
    condi = paste(df_germination$site, df_germination$plotID, sep = " "))

```

```{r}
df_germination <- df_germination %>% mutate(competition = df_germination$treat2)

df_germination <- df_germination %>% mutate(temperature = paste(df_germination$site, df_germination$treat1))

df_germination$temperature <- str_replace(df_germination$temperature, "LS ", "ambient LS")
df_germination$temperature <- str_replace(df_germination$temperature, "HS ambient", "ambient HS")
df_germination$temperature <- str_replace(df_germination$temperature, "HS warm", "warm HS") # that it match the format of the other file : single variable analysis


df_germination$temperature <- relevel(as.factor(df_germination$temperature), "ambient HS")
```
```{r}
df_germination <- df_germination %>%
  mutate(total_germinated = rowSums(df_germination[c("Day.0", "Day.2", "Day.4", "Day.6", "Day.8", "Day.12", "Day.16", "Day.24", "Day.32")], na.rm = TRUE))
#have to stop the mutate chaine: I will use total germinated

```

conversion for calculation later
```{r}
df_germination$Viability.test..number.tested<-as.numeric(df_germination[,"Viability.test..number.tested"])

df_germination$Viable.seeds<-as.numeric(df_germination[,"Viable.seeds"])
```

to deal with the flowers replicate per individual : do another data frame where you will do the mean of the replicates. in this table you will have the final germination percentages, T50%, ...
```{r}
df_percentage <- df_germination[!duplicated(df_germination$merge_ID), ] # ok : some replicate number are still != from 1, but that is because the replicate 2 was before the number 1. we have only 1 row per individual.
```

#calculating germination percentage
```{r}
df_percentage <- df_percentage %>% 
 mutate(germination_percentage = 100 * df_percentage$total_germinated  /    df_percentage$Number.of.seeds.for.germination)



```

```{r}
# replicate
replicate <- row.names(df_germination[duplicated(df_germination$merge_ID), ])


                                          


df_percentage <- df_percentage %>% mutate(percent_germinated_and_viable = 100 * df_percentage$total_germinated / df_percentage$Number.of.seeds.for.germination) #initialisation

for (i in replicate) {
  merge_ID_rep <- df_germination[i, "merge_ID"]


  df_rep <- df_germination[df_germination$merge_ID == merge_ID_rep, ]

  row_merge <- colSums(df_rep[c("Day.0", "Day.2", "Day.4", "Day.6", "Day.8", "Day.12", "Day.16", "Day.24", "Day.32")], na.rm = TRUE)

  df_percentage[df_percentage$merge_ID == merge_ID_rep, c("Day.0", "Day.2", "Day.4", "Day.6", "Day.8", "Day.12", "Day.16", "Day.24", "Day.32")] <- row_merge / nrow(df_rep) # replace the row of merge ID rep with the mean of all the replicates of this individual #working

  # same problem with viability data
  df_percentage[df_percentage$merge_ID == merge_ID_rep, "Viability.test..number.tested"] <- colSums(df_rep["Viability.test..number.tested"], na.rm = TRUE) / sum(!is.na(df_rep["Viability.test..number.tested"]))

  df_percentage[df_percentage$merge_ID == merge_ID_rep, "Viable.seeds"] <- colSums(df_rep["Viable.seeds"], na.rm = TRUE) / sum(!is.na(df_rep["Viable.seeds"]))
  

  df_percentage[df_percentage$merge_ID == merge_ID_rep, "Number.of.seeds.for.germination"] <- colSums(df_rep["Number.of.seeds.for.germination"], na.rm = TRUE) / sum(!is.na(df_rep["Number.of.seeds.for.germination"]))
  
  df_percentage[df_percentage$merge_ID == merge_ID_rep, "percent_germinated_and_viable"] 
  
  germinated_viable<- sum(rowSums(df_rep[c("total_germinated", "Viable.seeds")], na.rm = TRUE),na.rm=TRUE)/ max(sum(!is.na(df_rep["total_germinated"])),sum(!is.na(df_rep["Viable.seeds"])))
  
  to_chose<-rowSums(df_rep[c("total_germinated", "Viable.seeds")],na.rm=TRUE)
  nb_germination_2<- sum(df_rep[which(!is.na(to_chose)),"Number.of.seeds.for.germination"],na.rm=TRUE) /sum(!is.na(to_chose)) 

    df_percentage[df_percentage$merge_ID == merge_ID_rep, "percent_germinated_and_viable"] <-100*germinated_viable/nb_germination_2 #WORKS!
                                                                                                            
}
# this time it seems ok, (some NA: sometimes everything germinated, so no test; other simply not tested. sum of na value : 18/225 : negligeable)
```
germination percentage= mean of germination percentage of all the replicate.
 percentage of germinated and viable seeds= this percentage for only 1 replicate per individual, as we have only 1 viability test per individual.

now we can update germination percentage and total germinated with the updapted germination records
```{r}
df_percentage <- df_percentage %>%
  mutate(total_germinated = rowSums(df_percentage[c("Day.0", "Day.2", "Day.4", "Day.6", "Day.8", "Day.12", "Day.16", "Day.24", "Day.32")], na.rm = TRUE))

df_percentage <- df_percentage %>% 
 mutate(germination_percentage = 100 * df_percentage$total_germinated  /    df_percentage$Number.of.seeds.for.germination)
```


!! we do not include the seeds that germinated before the beginning of the experiment, ie in the incubator
```{r}
my_t50 <- c()

for (i in row.names(df_percentage)) {
  my_t50 <- c(my_t50, df_percentage[i,c( "Day.2", "Day.4", "Day.6", "Day.8", "Day.12", "Day.16", "Day.24", "Day.32")] %>%
    replace(is.na(.), 0) %>%
    as.numeric() %>%
    t50(intervals = c(2, 4, 6, 8, 12, 16, 24, 32), method = c("farooq"))) # calcule T50 : when there is missing value in the table, mean =0
}

df_percentage <- df_percentage %>% mutate(t50 = my_t50 %>% replace(is.na(.), 0)) # row with only na have a t50 of na : meaning 0
```


 for now, we include the seeds that were molded: we don't know if they are molde because they were already dead. we will see with the viaibility test
 

#analyses:
as my second batch will not be ready on time for the report: don't integrate the germination data with all_trait_pca for single variable analysis: do it with df_percentage.
## germination percentage
### boxplot
```{r}
boxplot_sp_gp <- ggplot(df_percentage, aes(x = condi, y = germination_percentage)) +
  geom_violin(aes(fill = condi)) +
  facet_wrap(vars(species), nrow = 2, scales = "free") +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", size = 0.2, colour = "red") +
  ggtitle("germination percentage per species")

boxplot_sp_gp

boxplot_gp <- ggplot(df_percentage, aes(x = condi, y = germination_percentage)) +
  geom_violin(aes(fill = condi)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", colour = "red") +
  ggtitle("germination percentage")

boxplot_gp
```

makes sense that nothing is significant
### glmm 
```{r}
glmm_gp1 <- glmer(germination_percentage / 100 ~ condi + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)

glmm_gp2 <- glmer(germination_percentage / 100 ~ site + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)

glmm_gp3 <- glmer(germination_percentage / 100 ~ temperature + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)


glmm_gp4 <- glmer(germination_percentage / 100 ~ competition + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)


sjPlot::tab_model(glmm_gp1, show.intercept = T)
sjPlot::plot_model(glmm_gp1, show.values = TRUE, width = 0.1, title = "effect of treatment on germination percentage")


sjPlot::tab_model(glmm_gp2, show.intercept = T)
sjPlot::plot_model(glmm_gp2, show.values = TRUE, width = 0.1, title = "effect of transplantation on germination  percentage")

sjPlot::tab_model(glmm_gp3, show.intercept = T)
sjPlot::plot_model(glmm_gp3, show.values = TRUE, width = 0.1, title = "effect of warming on germination percentage")

sjPlot::tab_model(glmm_gp4, show.intercept = T)
sjPlot::plot_model(glmm_gp4, show.values = TRUE, width = 0.1, title = "effect of competition on germination percentage")
```
### interactions
```{r}
glmm_gp_tc <- glmer(germination_percentage / 100 ~ temperature * competition + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)


sjPlot::tab_model(glmm_gp_tc, show.intercept = T)
sjPlot::plot_model(glmm_gp_tc, show.values = TRUE, width = 0.1, title = "interactions of temperature and competition on germination percentage")
```
### post hoc analysis
```{r}
summary(glht(glmm_gp1, mcp(condi = "Tukey")))
```

### check model
```{r}
check_glmm_test <- check_model(glmm_gp1)
plot(check_glmm_test)
```
```{r}
plotSimulatedResiduals(glmm_gp1)
DHARMa::plotSimulatedResiduals (glmm_gp1)
```

dharma: cope with non normal distribution : it's another function. 

### final graph
```{r}
a <- lme4::fixef(glmm_gp1)
b <- as.data.frame(a)
rname <- gsub("condi", "", row.names(b)[-1])
b <- append(b[, ][-1], 0)
rname <- append(rname, "HS A")

# confidence interval
CI <- coef(summary(glmm_gp1))
CI_HSA <- CI[, "Std. Error"][1] / a[1] # à vérifier
CI <- as.data.frame(append(CI[, "Std. Error"][-1], CI_HSA))[, ]

df_plot <- data.frame(condi = rname, value = b)
df_plot <- df_plot %>% mutate(competition = c("Vegetation", "Bare", "Bare", "Vegetation", "Bare", "Vegetation"), temperature = c("High ambient", "High warm", "High ambient", "Low ambient", "Low ambient", "High warm"), CI = CI)



plot_final <- ggplot(df_plot, aes(x = competition, y = value, fill = temperature)) +
  geom_dotplot(binaxis = "y", dotsize = 2) +
  geom_path(aes(group = temperature, color = temperature)) +
  ylab("value of glmm") +
  ggtitle("Warming, transplantation and competition influence the germination percentage")
plot_final
```
###final graph with confidence interval
code adapted from 
https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#predictions-andor-confidence-or-prediction-intervals-on-predictions

```{r}
newdat <- expand.grid(
  competition = c("bare", "vege"),
  temperature = c("ambient HS", "warm HS", "ambient LS"),
  germination_percentage = 0
)

newdat$germination_percentage <- predict(glmm_gp_tc, newdat, re.form = NA)
mm <- model.matrix(terms(glmm_gp_tc), newdat)
## or newdat$distance <- mm %*% fixef(fm1)
pvar1 <- diag(mm %*% tcrossprod(vcov(glmm_gp_tc), mm))
tvar1 <- pvar1 + lme4::VarCorr(glmm_gp_tc)$Subject[1] ## must be adapted for more complex models
cmult <- 1.96 ## could use 1.96
newdat <- data.frame(
  newdat,
  plo = newdat$germination_percentage - cmult * sqrt(pvar1),
  phi = newdat$germination_percentage + cmult * sqrt(pvar1)
  #   , tlo = newdat$LDMC-cmult*sqrt(tvar1)
  #  , thi = newdat$LDMC+cmult*sqrt(tvar1)
)
# plot confidence
g0_gp <- ggplot(newdat, aes(x = competition, y = germination_percentage, colour = temperature)) +
  geom_path(aes(group = temperature, color = temperature), linewidth = 0.75, position = position_dodge(width = 0.15)) +
  geom_pointrange(aes(ymin = plo, ymax = phi), position = position_dodge(width = 0.15), linewidth = 0.75, size = 1) +
  xlab("Competition")

g0_gp <- ggdraw(add_sub(g0_gp, "Competition:NS Site:NS Temperature: NS"))

g0_gp
```

```{r}
pred_gp2<-ggpredict(glmm_gp_tc,terms=c("competition", "temperature"))
g0_gp2<-plot(pred_gp2) + ggtitle(" ") + geom_line(position = position_dodge(width = 0.25)) + geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(width = 0.25), linewidth = 0.75, size = 1) 
g0_gp2<-ggdraw(add_sub(g0_gp2, "Competition:NS Site:* Temperature: NS",size=11,y=0.65))
g0_gp2

```


## t50
### boxplot

creating the dataset from df_percentage. in some sample, no seeds germinated, the result of the formula is 0, whereas it should be NA : we will delete these rows

 sometimes, more than half of the seeds germinated before day 2: 12,7% of the individual, this is too much, we can't use the data I think

```{r}
df_t50<-df_percentage
delete<-df_t50[which(df_t50$total_germinated==0),]
df_t50<-df_percentage[!rownames(df_percentage) %in% row.names(delete),]

delete<-df_t50[which(df_t50$total_germinated-df_t50$Day.0==0)
,]
df_t50<-df_t50[!rownames(df_t50) %in% row.names(delete),]



```

```{r}
length(which(df_t50$t50==0))/nrow(df_t50)
```
test:
```{r}
df_t50<-df_t50[which(df_t50$t50!=0),]
```


```{r}
boxplot_sp_t50 <- ggplot(df_t50, aes(x = condi, y = t50)) +
  geom_violin(aes(fill = condi)) +
  facet_wrap(vars(species), nrow = 2, scales = "free") +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", size = 0.2, colour = "red") +
  ggtitle("t50 per species")

boxplot_sp_t50

boxplot_t50 <- ggplot(df_t50, aes(x = condi, y = t50)) +
  geom_violin(aes(fill = condi)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", colour = "red") +
  ggtitle("t50")

boxplot_t50
```

makes sense that nbothing is significant
### glmm 
```{r}
c <- min(df_t50[which(df_t50$t50 != 0), ]$t50) / 2
df_t50 <- df_t50 %>% mutate(t50_log = log(df_t50$t50 + c))

glmm_t501 <- lme4::lmer(t50 ~ condi + (1 | blockID) + (1 | species), data = df_t50)
glmm_t501_log <- lme4::lmer(t50_log ~ condi + (1 | blockID) + (1 | species), data = df_t50)


glmm_t502 <- lme4::lmer(t50 ~ site + (1 | blockID) + (1 | species), data = df_t50)

glmm_t503 <- lme4::lmer(t50 ~ temperature + (1 | blockID) + (1 | species), data = df_t50)


glmm_t504 <- lme4::lmer(t50 ~ competition + (1 | blockID) + (1 | species), data = df_t50)


sjPlot::tab_model(glmm_t501, show.intercept = T)
sjPlot::plot_model(glmm_t501, show.values = TRUE, width = 0.1, title = "effect of treatment on t50")

sjPlot::tab_model(glmm_t501_log, show.intercept = T)
sjPlot::plot_model(glmm_t501_log, show.values = TRUE, width = 0.1, title = "effect of treatment on t50_log")


sjPlot::tab_model(glmm_t502, show.intercept = T)
sjPlot::plot_model(glmm_t502, show.values = TRUE, width = 0.1, title = "effect of transplantation on t50")

sjPlot::tab_model(glmm_t503, show.intercept = T)
sjPlot::plot_model(glmm_t503, show.values = TRUE, width = 0.1, title = "effect of warming on t50")

sjPlot::tab_model(glmm_t504, show.intercept = T)
sjPlot::plot_model(glmm_t504, show.values = TRUE, width = 0.1, title = "effect of competition on t50")
```

```{r}
glmm_t50_gamma<- lme4::glmer(log(t50+1) ~ condi + (1 | blockID) + (1 | species), family = Gamma, data = df_t50)
glmm_t50_gamma_log<- lme4::glmer(t50 ~ condi + (1 | blockID) + (1 | species), family = Gamma(link="log"), data = df_t50)
sjPlot::tab_model(glmm_t50_gamma, show.intercept = T)
sjPlot::plot_model(glmm_t50_gamma, show.values = TRUE, width = 0.1, title = "effect of transplantation on t50")
```

### interactions
```{r}
c <- min(df_t50[which(df_t50$t50 != 0), ]$t50) / 2
df_t50 <- df_t50 %>% mutate(t50_log = log(df_t50$t50 + c))

glmm_t50_tc <- lme4::lmer(t50 ~ temperature * competition + (1 | blockID) + (1 | species), data = df_t50)

glmm_t50_log_tc <- lme4::lmer(t50_log ~ temperature * competition + (1 | blockID) + (1 | species), data = df_t50)


sjPlot::tab_model(glmm_t50_log_tc, show.intercept = T)
sjPlot::plot_model(glmm_t50_tc, show.values = TRUE, width = 0.1, title = "interactions of temperature and competition on t50")
```
### post hoc analysis
```{r}
summary(glht(glmm_t501_log, mcp(condi = "Tukey")))
```

### check model
```{r}
check_glmm_test <- check_model(glmm_t501)
plot(check_glmm_test)
```
tweedie : other distribution : possible alternative : google zero and gamma. see if it's valid. 
I have a too small variance and a zero value inflation.
```{r}
check_glmm_test <- check_model(glmm_t501_log)
plot(check_glmm_test)
```
```{r}

check_glmm_test <- check_model(glmm_t50_gamma_log)
plot(check_glmm_test)
```
using the log or inverse link function doesn't change anything in terms of the quality of the qqplot

on possibility to get ride of a gamma distribution with 0 value: tweedieGLMM


tweedieGLMM(t50 ~ condi + (1 | blockID) + (1 | species), data = df_t50)

=> we have to much value with more than half of the seeds that germinated before D2. should start the experiment ag

### final graph
```{r}
a <- lme4::fixef(glmm_t501)
b <- as.data.frame(a)
rname <- gsub("condi", "", row.names(b)[-1])
b <- append(b[, ][-1], 0)
rname <- append(rname, "HS A")

# confidence interval
CI <- coef(summary(glmm_t501))
CI_HSA <- CI[, "Std. Error"][1] / a[1] # à vérifier
CI <- as.data.frame(append(CI[, "Std. Error"][-1], CI_HSA))[, ]

df_plot <- data.frame(condi = rname, value = b)
df_plot <- df_plot %>% mutate(competition = c("Vegetation", "Bare", "Bare", "Vegetation", "Bare", "Vegetation"), temperature = c("High ambient", "High warm", "High ambient", "Low ambient", "Low ambient", "High warm"), CI = CI)



plot_final <- ggplot(df_plot, aes(x = competition, y = value, fill = temperature)) +
  geom_dotplot(binaxis = "y", dotsize = 2) +
  geom_path(aes(group = temperature, color = temperature)) +
  ylab("value of glmm") +
  ggtitle("Warming, transplantation and competition influence the t50")
plot_final
```
###final graph with confidence interval
```{r}
newdat <- expand.grid(
  competition = c("bare", "vege"),
  temperature = c("ambient HS", "warm HS", "ambient LS"),
  t50 = 0
)

newdat$t50 <- predict(glmm_t50_tc, newdat, re.form = NA)
mm <- model.matrix(terms(glmm_t50_tc), newdat)
## or newdat$distance <- mm %*% fixef(fm1)
pvar1 <- diag(mm %*% tcrossprod(vcov(glmm_t50_tc), mm))
tvar1 <- pvar1 + lme4::VarCorr(glmm_t50_tc)$Subject[1] ## must be adapted for more complex models
cmult <- 1.96 ## could use 1.96
newdat <- data.frame(
  newdat,
  plo = newdat$t50 - cmult * sqrt(pvar1),
  phi = newdat$t50 + cmult * sqrt(pvar1)
  #   , tlo = newdat$LDMC-cmult*sqrt(tvar1)
  #  , thi = newdat$LDMC+cmult*sqrt(tvar1)
)
# plot confidence
g0_t50 <- ggplot(newdat, aes(x = competition, y = t50, colour = temperature)) +
  geom_path(aes(group = temperature, color = temperature), linewidth = 0.75, position = position_dodge(width = 0.15)) +
  geom_pointrange(aes(ymin = plo, ymax = phi), position = position_dodge(width = 0.15), linewidth = 0.75, size = 1) +
  xlab("Competition")

g0_t50 <- ggdraw(add_sub(g0_t50, "Competition:NS Site:NS Temperature: NS"))

g0_t50
```



## viability percentage
problem: i now have only 1 viability test per individual, not matching the replicate we have for germination we had before. we have to do a new data frame
```{r}
df_viability <- df_germination
df_viability <- df_viability[which(df_viability$Viability.test..number.tested != 0), ] # ok

df_viability$Viable.seeds.percentage <- NULL

df_viability <- df_viability %>% mutate(viability_percentage = 100 * df_viability$Viable.seeds / df_viability$Viability.test..number.tested) # working
```


### boxplot
```{r}
boxplot_sp_vp <- ggplot(df_viability, aes(x = condi, y = viability_percentage)) +
  geom_violin(aes(fill = condi)) +
  facet_wrap(vars(species), nrow = 2, scales = "free") +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", size = 0.2, colour = "red") +
  ggtitle("viability_percentage per species")

boxplot_sp_vp

boxplot_vp <- ggplot(df_viability, aes(x = condi, y = viability_percentage)) +
  geom_violin(aes(fill = condi)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", colour = "red") +
  ggtitle("viability_percentage")

boxplot_vp
```

makes sense that nbothing is significant
### glmm 
```{r}
c <- min(df_viability[which(df_viability$viability_percentage != 0), ]$viability_percentage) / 2
df_viability <- df_viability %>% mutate(viability_percentage_log = log(df_viability$viability_percentage + c))

glmm_vp1 <- lme4::glmer(viability_percentage/100 ~ condi + (1 | blockID) + (1 | species), data = df_viability,family=binomial)

glmm_vp1_log <- lme4::lmer(viability_percentage_log ~ condi + (1 | blockID) + (1 | species),data = df_viability)


glmm_vp2 <- lme4::glmer(viability_percentage/100 ~ site + (1 | blockID) + (1 | species), data = df_viability, family=binomial)

glmm_vp3 <- lme4::glmer(viability_percentage/100 ~ temperature + (1 | blockID) + (1 | species), data = df_viability,family=binomial)


glmm_vp4 <- lme4::glmer(viability_percentage/100 ~ competition + (1 | blockID) + (1 | species), data = df_viability,family=binomial)


sjPlot::tab_model(glmm_vp1, show.intercept = T)
sjPlot::plot_model(glmm_vp1, show.values = TRUE, width = 0.1, title = "effect of treatment on viability_percentage")

sjPlot::tab_model(glmm_vp1_log, show.intercept = T)
sjPlot::plot_model(glmm_vp1_log, show.values = TRUE, width = 0.1, title = "effect of treatment on viability_percentage_log")


sjPlot::tab_model(glmm_vp2, show.intercept = T)
sjPlot::plot_model(glmm_vp2, show.values = TRUE, width = 0.1, title = "effect of transplantation on viability_percentage")

sjPlot::tab_model(glmm_vp3, show.intercept = T)
sjPlot::plot_model(glmm_vp3, show.values = TRUE, width = 0.1, title = "effect of warming on viability_percentage")

sjPlot::tab_model(glmm_vp4, show.intercept = T)
sjPlot::plot_model(glmm_vp4, show.values = TRUE, width = 0.1, title = "effect of competition on viability_percentage")
```
### interactions
```{r}
c <- min(df_viability[which(df_viability$viability_percentage != 0), ]$viability_percentage) / 2
df_viability <- df_viability %>% mutate(viability_percentage_log = log(df_viability$viability_percentage + c))

glmm_vp_tc <- lme4::glmer(viability_percentage/100 ~ temperature * competition + (1 | blockID) + (1 | species), family=binomial, data = df_viability)

glmm_vp_log_tc <- lme4::lmer(viability_percentage_log ~ temperature * competition + (1 | blockID) + (1 | species), data =df_viability )


sjPlot::tab_model(glmm_vp_tc, show.intercept = T)
sjPlot::plot_model(glmm_vp_tc, show.values = TRUE, width = 0.1, title = "interactions of temperature and competition on viability_percentage")
```
### post hoc analysis
```{r}
summary(glht(glmm_vp1, mcp(condi = "Tukey")))
```

### check model
```{r}
check_glmm_test <- check_model(glmm_vp1)
plot(check_glmm_test)
```

much better than the gaussian
```{r}
#check_glmm_test <- check_model(glmm_vp1_log)
#plot(check_glmm_test)
#no sense
```

### final graph
```{r}
a <- lme4::fixef(glmm_vp1)
b <- as.data.frame(a)
rname <- gsub("condi", "", row.names(b)[-1])
b <- append(b[, ][-1], 0)
rname <- append(rname, "HS A")

# confidence interval
CI <- coef(summary(glmm_vp1))
CI_HSA <- CI[, "Std. Error"][1] / a[1] # à vérifier
CI <- as.data.frame(append(CI[, "Std. Error"][-1], CI_HSA))[, ]

df_plot <- data.frame(condi = rname, value = b)
df_plot <- df_plot %>% mutate(competition = c("Vegetation", "Bare", "Bare", "Vegetation", "Bare", "Vegetation"), temperature = c("High ambient", "High warm", "High ambient", "Low ambient", "Low ambient", "High warm"), CI = CI)



plot_final <- ggplot(df_plot, aes(x = competition, y = value, fill = temperature)) +
  geom_dotplot(binaxis = "y", dotsize = 2) +
  geom_path(aes(group = temperature, color = temperature)) +
  ylab("value of glmm") +
  ggtitle("Warming, transplantation and competition influence the viability_percentage")
plot_final
```
###final graph with confidence interval
```{r}
newdat <- expand.grid(
  competition = c("bare", "vege"),
  temperature = c("ambient HS", "warm HS", "ambient LS"),
  viability_percentage = 0
)

newdat$viability_percentage <- predict(glmm_vp_tc, newdat, re.form = NA)
mm <- model.matrix(terms(glmm_vp_tc), newdat)
## or newdat$distance <- mm %*% fixef(fm1)
pvar1 <- diag(mm %*% tcrossprod(vcov(glmm_vp_tc), mm))
tvar1 <- pvar1 + lme4::VarCorr(glmm_vp_tc)$Subject[1] ## must be adapted for more complex models
cmult <- 1.96 ## could use 1.96
newdat <- data.frame(
  newdat,
  plo = newdat$viability_percentage - cmult * sqrt(pvar1),
  phi = newdat$viability_percentage + cmult * sqrt(pvar1)
  #   , tlo = newdat$LDMC-cmult*sqrt(tvar1)
  #  , thi = newdat$LDMC+cmult*sqrt(tvar1)
)
# plot confidence
g0_vp <- ggplot(newdat, aes(x = competition, y = viability_percentage, colour = temperature)) +
  geom_path(aes(group = temperature, color = temperature), linewidth = 0.75, position = position_dodge(width = 0.15)) +
  geom_pointrange(aes(ymin = plo, ymax = phi), position = position_dodge(width = 0.15), linewidth = 0.75, size = 1) +
  xlab("Competition")

g0_vp <- ggdraw(add_sub(g0_vp, "Competition:NS Site:NS Temperature: NS"))

g0_vp
```
```{r}
pred_vp2<-ggpredict(glmm_vp_tc,terms=c("competition", "temperature"))
g0_vp2<-plot(pred_vp2) + ggtitle(" ") + geom_line(position = position_dodge(width = 0.25)) + geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(width = 0.25), linewidth = 0.75, size = 1) 
g0_vp2<-ggdraw(add_sub(g0_vp2, "Competition:NS Site:NS Temperature: NS",size=11,y=0.65))
g0_vp2

```
faire un dernier essai avec le pourcentage de graine viable initialement : somme de celle qui ont germé et qui on été testé viable

filtrer germination en gardant ceux ou tt à germer, et en ajoutant ceux ou nombre de tester est différent de 0

which(df_percentage$germinated_and_viable==0 & df_percentage$Viability.test..number.tested==0)
-> named integer(0)
so there is nothing to discard in df_percentage

do the models
## germination+ viable percentage
### boxplot
```{r}
boxplot_sp_gvp <- ggplot(df_percentage, aes(x = condi, y = percent_germinated_and_viable)) +
  geom_violin(aes(fill = condi)) +
  facet_wrap(vars(species), nrow = 2, scales = "free") +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", size = 0.2, colour = "red") +
  ggtitle("germination+viability percentage per species")

boxplot_sp_gvp

boxplot_gvp <- ggplot(df_percentage, aes(x = condi, y = percent_germinated_and_viable)) +
  geom_violin(aes(fill = condi)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", colour = "red") +
  ggtitle("germination+viability percentage")

boxplot_gvp
```

makes sense that nothing is significant
### glmm 
```{r}
glmm_gvp1 <- glmer(percent_germinated_and_viable / 100 ~ condi + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)

glmm_gvp2 <- glmer(percent_germinated_and_viable / 100 ~ site + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)

glmm_gvp3 <- glmer(percent_germinated_and_viable / 100 ~ temperature + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)


glmm_gvp4 <- glmer(percent_germinated_and_viable / 100 ~ competition + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)


sjPlot::tab_model(glmm_gvp1, show.intercept = T)
sjPlot::plot_model(glmm_gvp1, show.values = TRUE, width = 0.1, title = "effect of treatment on germination+viability percentage")


sjPlot::tab_model(glmm_gvp2, show.intercept = T)
sjPlot::plot_model(glmm_gvp2, show.values = TRUE, width = 0.1, title = "effect of transplantation on germination + viability percentage")

sjPlot::tab_model(glmm_gvp3, show.intercept = T)
sjPlot::plot_model(glmm_gvp3, show.values = TRUE, width = 0.1, title = "effect of warming on germination + viability percentage ")

sjPlot::tab_model(glmm_gvp4, show.intercept = T)
sjPlot::plot_model(glmm_gvp4, show.values = TRUE, width = 0.1, title = "effect of competition on germination+ viability percentage")
```
### interactions
```{r}
glmm_gvp_tc <- glmer(percent_germinated_and_viable / 100 ~ temperature * competition + (1 | blockID) + (1 | species), data = df_percentage, family = binomial)


sjPlot::tab_model(glmm_gvp_tc, show.intercept = T)
sjPlot::plot_model(glmm_gvp_tc, show.values = TRUE, width = 0.1, title = "interactions of temperature and competition on germination+ viability percentage")
```
### post hoc analysis
```{r}
summary(glht(glmm_gvp1, mcp(condi = "Tukey")))
```

### check model
```{r}
check_glmm_test <- check_model(glmm_gvp1)
plot(check_glmm_test)
```
```{r}
plotSimulatedResiduals(glmm_gvp1)
DHARMa::plotSimulatedResiduals (glmm_gvp1)
```
adapted from https://aosmith.rbind.io/2017/12/21/using-dharma-for-residual-checks-of-unsupported-models/#just-the-code-please
```{r}

sim_nbz = simulate(glmm_gvp1, nsim = 10)
str(sim_nbz)

sim_nbz = do.call(cbind, sim_nbz)
head(sim_nbz)

sim_res_nbz = createDHARMa(simulatedResponse = sim_nbz, 
                           observedResponse = df_percentage$percent_germinated_and_viable / 100,
                           fittedPredictedResponse = predict(glmm_gvp_tc),
                           integerResponse = TRUE)
plotSimulatedResiduals(sim_res_nbz)
```
bof: a vérifier
dharma: cope with non normal distribution : it's another function. 

### final graph
```{r}
a <- lme4::fixef(glmm_gvp1)
b <- as.data.frame(a)
rname <- gsub("condi", "", row.names(b)[-1])
b <- append(b[, ][-1], 0)
rname <- append(rname, "HS A")

# confidence interval
CI <- coef(summary(glmm_gvp1))
CI_HSA <- CI[, "Std. Error"][1] / a[1] # à vérifier
CI <- as.data.frame(append(CI[, "Std. Error"][-1], CI_HSA))[, ]

df_plot <- data.frame(condi = rname, value = b)
df_plot <- df_plot %>% mutate(competition = c("Vegetation", "Bare", "Bare", "Vegetation", "Bare", "Vegetation"), temperature = c("High ambient", "High warm", "High ambient", "Low ambient", "Low ambient", "High warm"), CI = CI)



plot_final <- ggplot(df_plot, aes(x = competition, y = value, fill = temperature)) +
  geom_dotplot(binaxis = "y", dotsize = 2) +
  geom_path(aes(group = temperature, color = temperature)) +
  ylab("value of glmm") +
  ggtitle("Warming, transplantation and competition influence the germination percentage")
plot_final
```
###final graph with confidence interval
code adapted from 
https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#predictions-andor-confidence-or-prediction-intervals-on-predictions

we are using a logit link function, the inverese is the logistic
logistic function= exp(x)*(1+exp(x))


```{r}
pred_gvp2<-ggpredict(glmm_gvp_tc,terms=c("competition", "temperature"))
g0_gvp2<-plot(pred_gvp2) + ggtitle(" ") + geom_line(position = position_dodge(width = 0.25)) + geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(width = 0.25), linewidth = 0.75, size = 1) 

ggdraw(add_sub(g0_gvp2, "Competition:NS Site:NS Temperature: NS"))
```

still not significant, we will see with my data


what to do on thursday : see lab copy book


t50()
x <- c(0, 0, 0, 0, 4, 17, 10, 7, 1, 0, 1, 0, 0, 0)
y <- c(0, 0, 0, 0, 4, 21, 31, 38, 39, 39, 40, 40, 40, 40)
int <- 1:length(x)

# From partial germination counts
#----------------------------------------------------------------------------
t50(germ.counts = x, intervals = int, method = "coolbear")
