---
title: "rangeX"
author: "Timothée Darbois"
date: "2024-03-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ade4)
library(ggplot2)
library(tidyverse)
library(googlesheets4)
library(dplyr)
library(rstatix)
library(readxl)
library(sjPlot)
library(contrast)
library(lme4)
library(lmerTest)
library (multcomp)
library(see)
library(performance)
library(broom.mixed)
library(ggeffects)

```

```{r}
df_Tim<-read.csv('D:/mes_documents/M1/stage/data/csv/rangeX seeds even number (2).xlsx - Feuille 1.csv',dec=",", na.strings = c("#DIV/0!"))

df_Tim<-as.data.frame(df_Tim)
df_Tim<- df_Tim %>% mutate(student='Timothée')

df_Tim<-df_Tim %>% mutate(condi=paste(df_Tim$site,df_Tim$plotID,sep=" "))

```

see how much data I have per species



```{r}
df_Tim<-df_Tim%>%
  filter(!is.na(weight.inf))
species=c("CC","CN","SP","TP","PS","PL","LM","SD","HM","LV")
select_species=c("CN","SP","TP","PS","PL","LM","LV") # with enough counts

#df_TP<-df1[df1$species=="TP",]
counts<-c()
for (i in species){
  print(i)
  counts<-c(counts,nrow(df_Tim[df_Tim$species==i,]))

}
count_data<-data.frame(species,counts)



ggplot(data=count_data,aes(x=species,y=counts)) +geom_bar(stat="identity") + ggtitle("timothee data")
```
simple boxplot: effect of treatments on seeds


## import of ingrid's data
```{r}
df_Ingrid<-read.csv('D:/mes_documents/M1/stage/data/csv/Copie de Seeds rangeX Timothée - Seeds odd numbers.csv', dec=",", na.strings = c("#DIV/0!"))
df_Ingrid<-as.data.frame(df_Ingrid)
df_Ingrid<- df_Ingrid %>% mutate(student='Ingrid')


```


data cleaning and raw data visualization
```{r}

df_Ingrid<-df_Ingrid%>%
  filter(!is.na(weight.inf))
counts<-c()
for (i in species){
  print(i)
  counts<-c(counts,nrow(df_Ingrid[df_Ingrid$species==i,]))

}
count_data<-data.frame(species,counts)



ggplot(data=count_data,aes(x=species,y=counts)) +geom_bar(stat="identity") +ggtitle('data_ingrid')

```

```{r}
df1<-df_Tim%>% dplyr::select(1,2,3,4,5,6,7,8,9,10,11,12,13,"flowers","seeds_number_1", "weight_1","seeds_number_2", "weight_2","seeds._number_3", "weight_3","student")
df2<-df_Ingrid%>% dplyr::select(1,2,3,4,5,6,7,8,9,10,11,12,13,"flowers","seeds_number_1", "weight_1","seeds_number_2", "weight_2","seeds._number_3", "weight_3","student")
df<-rbind(df1,df2)

df<-df %>% mutate(seeds_number.inf=as.integer(seeds_number.inf),       seeds_number_1=as.integer(seeds_number_1),seeds_number_2=as.integer(seeds_number_2),seeds._number_3=as.integer(seeds._number_3),weight.inf=as.numeric(weight.inf),weight.seed=as.numeric(weight.seed),flowers=as.numeric(flowers))
df<-df%>%
  filter(!is.na(weight.inf))

df<-df %>% mutate(condi=paste(df$site,df$plotID,sep=" "))

```
get the index of the column of seed number per infructescence, and add to df the column of total seed number/indiv (na.rm pour ignorer les na)
```{r}
column=c(grep("^seeds_number_1$", colnames(df)),grep("^seeds_number_2$", colnames(df)),grep("^seeds._number_3$", colnames(df)))

df<- df %>%
    rowwise() %>%
    mutate(seeds_number.indiv = sum(c_across(c("seeds_number_1","seeds_number_2","seeds._number_3")),na.rm=TRUE))
```

rowSums(dataframe[ , c(« column1 », « column2 », « column n »)])

construction de colonne weight.inf et weight.seed avec ajout d'une petite constante, pour pouvoir loger le tout
```{r}
c<-which(df$weight.inf!= 0)
c1<-min(df$weight.inf[c])/2

c<-which(df$weight.seed!= 0)
c2<-min(df$weight.seed[c])/2

c(c1,c2)
df<-data.frame(df,weight.inf.log=df$weight.inf+c1,weight.seed.log=df$weight.seed+c2)
```

construction d'une colone temperature avec warm high, ambient low, ambient high
```{r}
df<-data.frame(df,temperature=paste(df$treat1,df$site))
df$temperature<-str_replace(df$temperature,"LS","ambient LS")
```

for each species, seed number



```{r}
plot_snb<- ggplot(df, aes(x=condi, y=seeds_number.inf))+geom_violin(aes(fill=student))+
  geom_dotplot(binaxis = 'y',
        dotsize = 0.3,
        stackdir = 'center') +
    theme_classic() +
    geom_jitter(aes(colour = student), alpha=0.9, 
              position=position_jitter(w=0.1,h=0.1)) +
  facet_wrap(vars(species),nrow=2, scales='free')+
  ggtitle("seed number per infructescence")

plot_snb
```

for each species, seed weight
```{r}

plot_sw<- ggplot(df, aes(x=condi, y=weight.inf))+
  geom_boxplot(aes(fill=student)) +
  geom_dotplot(binaxis = 'y',
        dotsize = 1,
        stackdir = 'center') +
    theme_classic() + facet_wrap(vars(species),nrow=2,scales='free')+ggtitle("seed weight per infructescence")
  

plot_sw
```

for each species, weight per seeds
```{r}
plot_wps<- ggplot(df, aes(x=condi, y=log(weight.seed)))+geom_boxplot(aes(fill=student)) + geom_dotplot(binaxis = 'y',
        dotsize = 1,
        stackdir = 'center') +
    theme_classic() + facet_wrap(vars(species),nrow=2,scales='free')+ggtitle("seed weight per seed")
  

plot_wps
```

# analyse stat
## effet expérimentateur
```{r}
df_TP<-df[df$species=="TP",]
df_TP<-df_TP %>%
  filter(!is.na(weight.inf))


```

## qqplot seed weight
```{r}
plot_sw<- ggplot(df, aes(x= weight.inf))+geom_histogram(aes(fill=student))+
    theme_classic() + facet_wrap(vars(species),nrow=2,scales='free')+ggtitle("seed weight per infructescence")
plot_sw
  
```

## qqplot weight per infructescence
```{r}
hist_wpi<- ggplot(df, aes(x=weight.inf))+
  geom_histogram(aes(fill=student))+
    theme_classic() + 
  facet_wrap(vars(species),nrow=2,scales='free')+
  ggtitle("seed weight per infructescence")
hist_wpi
```


inutile:
shapiro.test(df$weight.seed)
shapiro.test(log(df$weight.seed+1))

shapiro.test(df$seeds_number.inf)

shapiro.test(log(df[df$species=="TP",]$weight.inf+1))
shapiro.test(df[df$species=="TP",]$weight.inf)


at least, some are not normal (eg : there are bimodal distribution with viable and not viable seeds)
#U test  effect of the experimentator
```{r}
U_sn<-c()
U_wpi<-c()
U_wps<-c()

for (i in 1:7){
  data_U<-df[df$species==select_species[i],]
  
  U_sn<-rbind(U_sn,wilcox.test(seeds_number.inf~student,data_U))

  U_wpi<-rbind(U_wpi,wilcox.test(weight.inf~student,data_U))

  U_wps<-rbind(U_wps,wilcox.test(weight.seed~student,data_U))
}

U_sn<-cbind(U_sn, select_species)
U_wpi<-cbind(U_wpi, select_species)
U_wps<-cbind(U_wps, select_species)

print("seeds number")
U_sn
print("weight.inf")
U_wpi
print("weight per seed")
U_wps
```
## pool all the species together, as part of a community.

```{r}
plot_t_sn<- ggplot(df, aes(x=condi, y=seeds_number.inf ))+geom_boxplot(aes(fill=student)) + geom_dotplot(binaxis = 'y',
        dotsize = 0.01,
        stackdir = 'center') +theme_classic() 
    
plot_t_sn
anova_test(df,seeds_number.inf~condi)
anova_test(df,seeds_number.inf~student)

```

```{r}
plot_t_sw<- ggplot(df, aes(x=condi, y=log(weight.inf) ))+geom_boxplot(aes(fill=student)) + geom_dotplot(binaxis = 'y',
        dotsize = 0.01,
        stackdir = 'center') +theme_classic() 
    
plot_t_sw
anova_test(df,weight.inf~condi)
anova_test(df,weight.inf~student)

```

```{r}
plot_t_wpi<- ggplot(df, aes(x=condi, y=log(weight.seed) ))+geom_boxplot(aes(fill=student)) + geom_dotplot(binaxis = 'y',
        dotsize = 0.01,
        stackdir = 'center') +theme_classic() 
    
plot_t_wpi
anova_test(df,weight.seed~condi)
anova_test(df,weight.inf~student)



```



anova 2 way test for student and conditions effect. there is no interactions between both.
```{r}
var=c(8,9,10)

anov_sn<-c()
anov_wpi<-c()
anov_wps<-c()

for (i in 1:7){
  test_anov<-df[df$species==select_species[i],]
  
  anov_sn<-rbind(anov_sn,anova_test(test_anov,seeds_number.inf~student*condi))

  anov_wpi<-rbind(anov_wpi,anova_test(test_anov,weight.inf~student*condi))

  anov_wps<-rbind(anov_wps,anova_test(test_anov,weight.seed~student*condi))
}

species_anov<-c()
for (i in 1:7){species_anov<-c(species_anov,rep(select_species[i],3))}
anov_sn<-data.frame(anov_sn,species=species_anov)
anov_wpi<-data.frame(anov_wpi,species=species_anov)
anov_wps<-data.frame(anov_wps,species=species_anov)
print(anov_sn)
print(anov_wpi)
print(anov_wps)

```
## lm


lm_allsp_sn <- lm(seeds_number.inf~condi, data=df,family= "poisson")
lm_allsp_sn
lm_allsp_sn2 <- lm(seeds_number.inf~site, data=df,family= "poisson")


sjPlot::tab_model(lm_allsp_sn,show.intercept = T)
plot_model(lm_allsp_sn, show.values = TRUE, width = 0.1, title = "effect of treatments on seeds number per infructescence") 

qqnorm(lm_allsp_sn$residuals,main="normal residuals qqplot seed number per inf")
qqline(lm_allsp_sn$residuals)
qqnorm(log(lm_allsp_sn$residuals),main="log(residuals) qqplot seed number per inf")
qqline(log(lm_allsp_sn$residuals))

## glm
### seed number



#glm_allsp_sn <- glm(seeds_number.inf+0.0001~condi,data=df,family=Gamma(link=inverse))
glm_allsp_sn <- glm(seeds_number.inf~condi,data=df,family="poisson")
glm_allsp_sn
glm_allsp_sn2 <- glm(seeds_number.inf~site, data=df,family= "poisson")
glm_allsp_sn3 <- glm(seeds_number.inf~temperature, data=df,family= "poisson")
glm_allsp_sn4 <- glm(seeds_number.inf~treat2, data=df,family= "poisson")


sjPlot::tab_model(glm_allsp_sn,show.intercept = T)
plot_model(glm_allsp_sn, show.values = TRUE, width = 0.1, title = "effect of treatments on seeds number per infructescence") 

sjPlot::tab_model(glm_allsp_sn2,show.intercept = T)
plot_model(glm_allsp_sn2, show.values = TRUE, width = 0.1, title = "effect of transplantation on seeds number per infructescence") 

sjPlot::tab_model(glm_allsp_sn3,show.intercept = T)
plot_model(glm_allsp_sn3, show.values = TRUE, width = 0.1, title = "effect of warming on seeds number per infructescence") 

sjPlot::tab_model(glm_allsp_sn3,show.intercept = T)
plot_model(glm_allsp_sn4, show.values = TRUE, width = 0.1, title = "effect of competition on seeds number per infructescence") 

### weight per infructescence

glm_allsp_wpi <- glm(log(weight.inf.log)~condi, data=df)
glm_allsp_wpi
glm_allsp_wpi2 <- glm(log(weight.inf.log)~site, data=df)
glm_allsp_wpi3 <- glm(log(weight.inf.log)~temperature, data=df)
glm_allsp_wpi4 <- glm(log(weight.inf.log)~treat2, data=df)


sjPlot::tab_model(glm_allsp_wpi,show.intercept = T)
plot_model(glm_allsp_wpi, show.values = TRUE, width = 0.1, title = "effect of treatments on seed weight per infructescence") 

sjPlot::tab_model(glm_allsp_wpi2,show.intercept = T)
plot_model(glm_allsp_wpi2, show.values = TRUE, width = 0.1, title = "effect of transplantation on seed weight per infructescence") 

sjPlot::tab_model(glm_allsp_wpi3,show.intercept = T)
plot_model(glm_allsp_wpi3, show.values = TRUE, width = 0.1, title = "effect of warming on seed weight per infructescence") 

sjPlot::tab_model(glm_allsp_wpi3,show.intercept = T)
plot_model(glm_allsp_wpi4, show.values = TRUE, width = 0.1, title = "effect of competition on seeds number per infructescence") 


let's focus on PL

df_PL<- df[df$species== "PL",]
glm_PL_wpi <- glm(log(weight.inf.log)~condi, data=df_PL)
summary(glm_PL_wpi)
glm_PL_wpi2 <- glm(log(weight.inf.log)~site, data=df_PL)
summary(glm_PL_wpi2 )
glm_PL_wpi3 <- glm(log(weight.inf.log)~temperature, data=df_PL)


sjPlot::tab_model(glm_PL_wpi,show.intercept = T)
plot_model(glm_PL_wpi, show.values = TRUE, width = 0.1, title = "effect of treatments on seeds number per infructescence") 
sjPlot::tab_model(glm_PL_wpi2,show.intercept = T)
plot_model(glm_PL_wpi2, show.values = TRUE, width = 0.1, title = "effect of transplantation on seeds number per infructescence") 

sjPlot::tab_model(glm_PL_wpi3,show.intercept = T)
plot_model(glm_PL_wpi3, show.values = TRUE, width = 0.1, title = "effect of temperature on seeds number per infructescence") 

### weight per seed

glm_allsp_wps <- glm(log(weight.seed.log)~condi, data=df)
glm_allsp_wps
glm_allsp_wps2 <- glm(log(weight.seed.log)~site, data=df)
glm_allsp_wps3 <- glm(log(weight.seed.log)~temperature, data=df)
glm_allsp_wps4 <- glm(log(weight.seed.log)~treat2, data=df)


sjPlot::tab_model(glm_allsp_wps,show.intercept = T)
plot_model(glm_allsp_wps, show.values = TRUE, width = 0.1, title = "effect of treatments on seed weight per seed") 

sjPlot::tab_model(glm_allsp_wps2,show.intercept = T)
plot_model(glm_allsp_wps2, show.values = TRUE, width = 0.1, title = "effect of transplantation on seed weight per seed") 

sjPlot::tab_model(glm_allsp_wps3,show.intercept = T)
plot_model(glm_allsp_wps3, show.values = TRUE, width = 0.1, title = "effect of warming on seed weight per seed") 

sjPlot::tab_model(glm_allsp_wps3,show.intercept = T)
plot_model(glm_allsp_wps4, show.values = TRUE, width = 0.1, title = "effect of competition on seed weight per seed") 

their might be a problem because my numbers are so small.

QQplot

  
  
qqnorm(glm_allsp_wpi$residuals,main="normal residuals qqplot seed number per inf")
qqline(glm_allsp_wpi$residuals)
qqnorm(log(glm_allsp_wpi$residuals),main="log(residuals) qqplot seed number per inf")
qqline(log(glm_allsp_wpi$residuals))

looks not so bad. maybe we should delete some outbreakers. 


qqnorm(log(glm_PL_wpi$residuals),main="log(residuals) qqplot PL seed number per inf")
qqline(log(glm_PL_wpi$residuals))

seed number with block and species random effect
#glmm

##seed number
```{r}
#glmm_sn1<- glmer(seeds_number.indiv~condi +  (1|blockID)+ (1|species), data=df,family= poisson, offset=flowers)

#releveling temperature
df$temp<-relevel(as.factor(df$temperature),"ambient HS")
levels(df$temp)

glmm_sn1<- glmer.nb(seeds_number.inf~condi + (1|blockID)+ (1|species), data=df)
#gllm_test<-glmer.nb(seeds_number.inf~condi + (1|blockID)+ (1|species), data=df)

glmm_sn2<- glmer.nb(seeds_number.inf~site + (1|blockID)+ (1|species), data=df)

glmm_sn3<- glmer.nb(seeds_number.inf~temp +  (1|blockID)+ (1|species), data=df)


glmm_sn4<- glmer.nb(seeds_number.inf~treat2 +  (1|blockID)+ (1|species), data=df)


sjPlot::tab_model(glmm_sn1,show.intercept = T)
sjPlot::plot_model(glmm_sn1, show.values = TRUE, width = 0.1, title = "effect of treatment on seed number per infructescence")


sjPlot::tab_model(glmm_sn2,show.intercept = T)
sjPlot::plot_model(glmm_sn2, show.values = TRUE, width = 0.1, title = "effect of transplantation on seeds number per infructescence") 

sjPlot::tab_model(glmm_sn3,show.intercept = T)
plot_model(glmm_sn3, show.values = TRUE, width = 0.1, title = "effect of warming on seeds number per infructescence") 

sjPlot::tab_model(glmm_sn4,show.intercept = T)
plot_model(glmm_sn4, show.values = TRUE, width = 0.1, title = "effect of competition on seeds number per infructescence") 
```
perhaps for the effect of temperature, I should add the others variable as random effect?

visualisation of the random effect
```{r}
rr<-ranef(glmm_sn1,condVar=TRUE)
aa<-broom::augment(rr)
g1 <- ggplot(aa,aes(estimate,level,xmin=lb,xmax=ub))+
         geom_errorbarh(height=0)+
         geom_vline(xintercept=0,lty=2)+
         geom_point()
g1
```
how do I interpret this?
                      
### post hoc analysis
```{r}
summary(glht(glmm_sn1, mcp(condi="Tukey")))

```



### check performance

```{r}
check_glmm_sn1<-check_model(glmm_sn1)
plot(check_glmm_sn1)
```


```{r}
check_overdispersion(glmm_sn1)

```
final graph
```{r}
a<-fixef(glmm_sn1)
b<-as.data.frame(a)
rname<- gsub("condi", "", row.names(b)[-1])
b<-append(b[,][-1],0)
rname<-append(rname,"HS A")

#confidence interval
CI<-coef(summary(glmm_sn1))
CI_HSA<-CI[,"Std. Error"][1]/a[1] #à vérifier
CI<-as.data.frame(append(CI[,"Std. Error"][-1],CI_HSA))[,]

df_plot<-data.frame(condi=rname,value=b)
df_plot<-df_plot %>%mutate(competition=c("Vegetation","Bare","Bare","Vegetation", "Bare", "Vegetation"),temperature= c("High ambient", "High warm", "High ambient", "Low ambient", "Low ambient", "High warm"),CI=CI)



plot_final<-ggplot(df_plot,aes(x=competition,y=value,fill=temperature))+
  geom_dotplot(binaxis='y',dotsize = 2)+
  geom_path(aes(group = temperature, color = temperature))+
  ylab("value of glmm")+
  ggtitle("Warming, transplantation and competition influence seed number per infructescence")
plot_final

```

```{r}
preds <- broom::augment(glmm_sn1, newdata = tibble(condi = df$condi), se_fit= TRUE, type.predict = "link") |> mutate(.upper = exp(.fitted + 1.96 * .sqrtXwt), .lower = exp(.fitted - 1.96 * .sqrtXwt), .fitted = exp(.fitted))

preds
```
ggpredict : NS
```{r}
plot(ggpredict(glmm_sn1, terms = "condi"))
```


### interaction between variables for seed number
#### temperature*competition
NS
```{r}
glmm_sn_tc<- glmer.nb(seeds_number.inf~temp*treat2 + (1|blockID)+ (1|species), data=df)


sjPlot::tab_model(glmm_sn_tc,show.intercept = T)
plot_model(glmm_sn_tc, show.values = TRUE, width = 0.1, title = "interactions of temperature and competition on seeds number per infructescence") 
```
anova type 2, 3?

```{r}
Anova(glmm_sn_tc)
Anova(glmm_sn_tc, type = 3)
```

#### transplantation*competition
```{r}
glmm_sn_sc<- glmer.nb(seeds_number.inf~site*treat2 + (1|blockID)+ (1|species), data=df)


sjPlot::tab_model(glmm_sn_sc,show.intercept = T)
plot_model(glmm_sn_sc, show.values = TRUE, width = 0.1, title = "interaction of site and competition on seeds number per infructescence") 
```
```{r}
Anova(glmm_sn_sc, type = 2)
Anova(glmm_sn_sc, type = 3)
```
test per species
TP: NS
```{r}
glmm_sn_TP<- glmer.nb(seeds_number.inf~condi + (1|blockID), data=df[df$species=="TP",])

sjPlot::tab_model(glmm_sn_TP,show.intercept = T)
sjPlot::plot_model(glmm_sn_TP, show.values = TRUE, width = 0.1, title = "effect of treatment on TP seed number per infructescence")


summary(glht(glmm_sn_TP, mcp(condi="Tukey")))
```
CN: NS
```{r}
glmm_sn_CN<- glmer.nb(seeds_number.inf~condi + (1|blockID), data=df[df$species=="CN",])

sjPlot::tab_model(glmm_sn_CN,show.intercept = T)
sjPlot::plot_model(glmm_sn_CN, show.values = TRUE, width = 0.1, title = "effect of treatment on TP seed number per infructescence")


summary(glht(glmm_sn_CN, mcp(condi="Tukey")))
```
SP: nothing significant
```{r}
glmm_sn_SP<- glmer.nb(seeds_number.inf~condi + (1|blockID), data=df[df$species=="SP",])

sjPlot::tab_model(glmm_sn_SP,show.intercept = T)
sjPlot::plot_model(glmm_sn_SP, show.values = TRUE, width = 0.1, title = "effect of treatment on SP seed number per infructescence")


summary(glht(glmm_sn_SP, mcp(condi="Tukey")))
```

LV: nothing significant
```{r}
glmm_sn_LV<- glmer.nb(seeds_number.inf~condi + (1|blockID), data=df[df$species=="LV",])

sjPlot::tab_model(glmm_sn_LV,show.intercept = T)
sjPlot::plot_model(glmm_sn_LV, show.values = TRUE, width = 0.1, title = "effect of treatment on LV seed number per infructescence")


summary(glht(glmm_sn_LV, mcp(condi="Tukey")))
```

PL: effect of transplantation in high site
```{r}
glmm_sn_PL<- glmer.nb(seeds_number.inf~condi + (1|blockID), data=df[df$species=="PL",])
glmm_sn2_PL<- glmer.nb(seeds_number.inf~site + (1|blockID), data=df[df$species=="PL",])

glmm_sn3_PL<- glmer.nb(seeds_number.inf~temp +  (1|blockID), data=df[df$species=="PL",])


glmm_sn4_PL<- glmer.nb(seeds_number.inf~treat2 +  (1|blockID), data=df[df$species=="PL",])

sjPlot::tab_model(glmm_sn_PL,show.intercept = T)
sjPlot::plot_model(glmm_sn_PL, show.values = TRUE, width = 0.1, title = "effect of treatment on PL seed number per infructescence")

sjPlot::tab_model(glmm_sn2_PL,show.intercept = T)
sjPlot::plot_model(glmm_sn2_PL, show.values = TRUE, width = 0.1, title = "effect of transplantation on PL seeds number per infructescence") 

sjPlot::tab_model(glmm_sn3_PL,show.intercept = T)
plot_model(glmm_sn3_PL, show.values = TRUE, width = 0.1, title = "effect of warming on PL seeds number per infructescence") 

sjPlot::tab_model(glmm_sn4_PL,show.intercept = T)
plot_model(glmm_sn4_PL, show.values = TRUE, width = 0.1, title = "effect of competition on PL seeds number per infructescence") 



summary(glht(glmm_sn_PL, mcp(condi="Tukey")))
```
LM:effect of competition
```{r}
glmm_sn1_LM<- glmer.nb(seeds_number.inf~condi + (1|blockID), data=df[df$species=="LM",])



glmm_sn2_LM<- glmer.nb(seeds_number.inf~site + (1|blockID), data=df[df$species=="LM",])

glmm_sn3_LM<- glmer.nb(seeds_number.inf~temp +  (1|blockID), data=df[df$species=="LM",])


glmm_sn4_LM<- glmer.nb(seeds_number.inf~treat2 +  (1|blockID), data=df[df$species=="LM",])

sjPlot::tab_model(glmm_sn1_LM,show.intercept = T)
sjPlot::plot_model(glmm_sn1_LM, show.values = TRUE, width = 0.1, title = "effect of treatment on LM seed number per infructescence")

sjPlot::tab_model(glmm_sn2_LM,show.intercept = T)
sjPlot::plot_model(glmm_sn2_LM, show.values = TRUE, width = 0.1, title = "effect of transplantation on LM seeds number per infructescence") 

sjPlot::tab_model(glmm_sn3_LM,show.intercept = T)
plot_model(glmm_sn3_LM, show.values = TRUE, width = 0.1, title = "effect of warming on LM seeds number per infructescence") 

sjPlot::tab_model(glmm_sn4_LM,show.intercept = T)
plot_model(glmm_sn4_LM, show.values = TRUE, width = 0.1, title = "effect of competition on LM seeds number per infructescence") 
```

```{r}
summary(glht(glmm_sn1_LM, mcp(condi="Tukey")))

```

```{r}
a<-fixef(glmm_sn1_LM)
b<-as.data.frame(a)
rname<- gsub("condi", "", row.names(b)[-1])
b<-append(b[,][-1],0)
rname<-append(rname,"HS A")

#confidence interval
CI<-coef(summary(glmm_sn1_LM))
CI_HSA<-CI[,"Std. Error"][1]/a[1] #à vérifier
CI<-as.data.frame(append(CI[,"Std. Error"][-1],CI_HSA))[,]

df_plot<-data.frame(condi=rname,value=b)
df_plot<-df_plot %>%mutate(competition=c("Vegetation","Bare","Bare","Vegetation", "Bare", "Vegetation"),temperature= c("High ambient", "High warm", "High ambient", "Low ambient", "Low ambient", "High warm"),CI=CI)



plot_final<-ggplot(df_plot,aes(x=competition,y=value,fill=temperature))+
  geom_dotplot(binaxis='y',dotsize = 2)+
  geom_path(aes(group = temperature, color = temperature))+
  ylab("value of glmm")+
  ggtitle("Warming, transplantation and competition influence seed number per infructescence")
plot_final

```
PS:NS
```{r}
glmm_sn_PS<- glmer.nb(seeds_number.inf~condi + (1|blockID), data=df[df$species=="PS",])

sjPlot::tab_model(glmm_sn_PS,show.intercept = T)
sjPlot::plot_model(glmm_sn_PS, show.values = TRUE, width = 0.1, title = "effect of treatment on PS seed number per infructescence")


summary(glht(glmm_sn_PS, mcp(condi="Tukey")))
```


## seed weight per seed

```{r}
glmm_wps1<- lmer(log(weight.seed.log)~condi + (1|blockID)+ (1|species), data=df)
# log distribution : no need of generalized

glmm_wps2<- lmer(log(weight.seed.log)~site + (1|blockID)+ (1|species), data=df)

glmm_wps3<- lmer(log(weight.seed.log)~temp + (1|blockID)+ (1|species), data=df)

glmm_wps4<- lmer(log(weight.seed.log)~treat2 + (1|blockID)+ (1|species), data=df)



sjPlot::tab_model(glmm_wps1,show.intercept = T)
plot_model(glmm_wps1, show.values = TRUE, width = 0.1, title = "effect of treatments on seed weight ")  

sjPlot::tab_model(glmm_wps2,show.intercept = T)
plot_model(glmm_wps2, show.values = TRUE, width = 0.1, title = "effect of transplantation on seeds weight ") 

sjPlot::tab_model(glmm_wps3,show.intercept = T)
plot_model(glmm_wps3, show.values = TRUE, width = 0.1, title = "effect of warming on seeds weight ") 

sjPlot::tab_model(glmm_wps4,show.intercept = T)
plot_model(glmm_wps4, show.values = TRUE, width = 0.1, title = "effect of competition on seeds weight ") 
```

```{r}
summary(glht(glmm_wps1, mcp(condi="Tukey")))

```

### check model
```{r}
plot(check_model(glmm_wps1, detrend= FALSE))
```
#### final plot
```{r}
aw<-fixef(glmm_wps1)
bw<-as.data.frame(aw)
rnamew<- gsub("condi", "", row.names(bw)[-1])
bw<-append(bw[,][-1],0)
rnamew<-append(rnamew,"HS A")

#confidence interval
CIw<-coef(summary(glmm_sn1))
CI_HSAw<-CIw[,"Std. Error"][1]/a[1] #à vérifier
CIw<-as.data.frame(append(CIw[,"Std. Error"][-1],CI_HSAw))[,]

df_plotw<-data.frame(condi=rnamew,value=bw)
df_plotw<-df_plotw %>%mutate(competition=c("Vegetation","Bare","Bare","Vegetation", "Bare", "Vegetation"),temperature= c("High ambient", "High warm", "High ambient", "Low ambient", "Low ambient", "High warm"),CI=CIw)



plot_finalw<-ggplot(df_plotw,aes(x=competition,y=value,fill=temperature))+
  geom_dotplot(binaxis='y',dotsize = 2)+
  geom_path(aes(group = temperature, color = temperature))+
  ylab("value of glmm")+
  ggtitle("Only the transplantation has an effect on seed weight ")
plot_finalw

```



## effect of interactions between variables on seed weight
### temperature * competition
```{r}
glmm_wps_tc<- lmer(log(weight.seed.log)~temp*treat2 + (1|blockID)+ (1|species), data=df)


sjPlot::tab_model(glmm_wps_tc,show.intercept = T)
plot_model(glmm_wps_tc, show.values = TRUE, width = 0.1, title = "interactions of temperature and competition on seeds number per infructescence") 
```
? how could I do this. what 's the difference between type II and III
```{r}
Anova(glmm_wps_tc, type = 2)
Anova(glmm_wps_tc, type = 3)
```

##final graph with confidence interval
glmm_wps_tc<- lmer(log(weight.seed.log)~temp*treat2 + (1|blockID)+ (1|species), data=df)

```{r}
newdat <- expand.grid(
    treat2.y=c("bare","vege")
    , temp=c("ambient HS","warm HS", " ambient LS")
    ,no_rep_stems = 0
)

newdat$log(weight.seed.log) <- predict(glmm_wps_tc,newdat,re.form=NA)
mm <- model.matrix(terms(glmm_wps_tc),newdat)
## or newdat$distance <- mm %*% fixef(fm1)
pvar1 <- diag(mm %*% tcrossprod(vcov(glmm_wps_tc),mm))
tvar1 <- pvar1+VarCorr(glmm_wps_tc)$Subject[1]  ## must be adapted for more complex models
cmult <- 1.96 ## could use 1.96
newdat <- data.frame(
    newdat
    , plo = newdat$log(weight.seed.log)-cmult*sqrt(pvar1)
    , phi = newdat$log(weight.seed.log)+cmult*sqrt(pvar1)
 #   , tlo = newdat$LDMC-cmult*sqrt(tvar1)
  #  , thi = newdat$LDMC+cmult*sqrt(tvar1)
)
#plot confidence
g0_wps <- ggplot(newdat, aes(x=treat2.y, y=log(weight.seed.log), colour=temp)) +
  geom_path(aes(group = temp, color = temp),linewidth=0.75,position = position_dodge(width = 0.15))+
  geom_pointrange(aes(ymin = plo, ymax = phi),position = position_dodge(width = 0.15), linewidth=0.75, size=1)+
  xlab("Competition")+
  ylab("log(seed weight)")

g0_wps
```

```{r}
#summary(glht(glmm_sn_tc, mcp(temperature="Tukey",treat2="Tukey")))

```

temperature*site : aucun sens

glmm_sn_ts<- glmer(seeds_number.inf~site*temp + (1|blockID)+ (1|species), data=df,family= poisson)


sjPlot::tab_model(glmm_sn_ts,show.intercept = T)
plot_model(glmm_sn_ts, show.values = TRUE, width = 0.1, title = "interaction of temperature and site on seeds number per infructescence") 

site*competition
```{r}
glmm_wps_sc<- lmer(log(weight.seed.log)~site*treat2 + (1|blockID)+ (1|species), data=df)


sjPlot::tab_model(glmm_wps_sc,show.intercept = T)
plot_model(glmm_wps_sc, show.values = TRUE, width = 0.1, title = "interaction of site and competition on seeds weight per infructescence") 
```
```{r}
Anova(glmm_wps_sc, type = 2)
Anova(glmm_wps_sc, type = 3)
```

### test per species
TP: NS
```{r}
glmm_wps_TP<- lmer(log(weight.seed.log)~condi + (1|blockID), data=df[df$species=="TP",])

sjPlot::tab_model(glmm_wps_TP,show.intercept = T)
sjPlot::plot_model(glmm_wps_TP, show.values = TRUE, width = 0.1, title = "effect of treatment on TP seed number per infructescence")


summary(glht(glmm_wps_TP, mcp(condi="Tukey")))
```
CN: NS
```{r}
glmm_wps_CN<- lmer(log(weight.seed.log)~condi + (1|blockID), data=df[df$species=="CN",])

sjPlot::tab_model(glmm_wps_CN,show.intercept = T)
sjPlot::plot_model(glmm_wps_CN, show.values = TRUE, width = 0.1, title = "effect of treatment on TP seed number per infructescence")


summary(glht(glmm_wps_CN, mcp(condi="Tukey")))
```
SP: effect of competition 
```{r}
glmm_wps_SP<- lmer(log(weight.seed.log)~condi + (1|blockID), data=df[df$species=="SP",])

sjPlot::tab_model(glmm_wps_SP,show.intercept = T)
sjPlot::plot_model(glmm_wps_SP, show.values = TRUE, width = 0.1, title = "effect of treatment on SP seed number per infructescence")


summary(glht(glmm_wps_SP, mcp(condi="Tukey")))
```

LV: nothing significant
```{r}
glmm_wps_LV<- lmer(log(weight.seed.log)~condi + (1|blockID), data=df[df$species=="LV",])

sjPlot::tab_model(glmm_wps_LV,show.intercept = T)
sjPlot::plot_model(glmm_wps_LV, show.values = TRUE, width = 0.1, title = "effect of treatment on LV seed number per infructescence")


summary(glht(glmm_wps_LV, mcp(condi="Tukey")))
```

PL: effect of transplantation in high site
```{r}
glmm_wps_PL<- lmer(log(weight.seed.log)~condi + (1|blockID), data=df[df$species=="PL",])
glmm_wps2_PL<- lmer(log(weight.seed.log)~site + (1|blockID), data=df[df$species=="PL",])

glmm_wps3_PL<- lmer(log(weight.seed.log)~temp +  (1|blockID), data=df[df$species=="PL",])


glmm_wps4_PL<- lmer(log(weight.seed.log)~treat2 +  (1|blockID), data=df[df$species=="PL",])

sjPlot::tab_model(glmm_wps_PL,show.intercept = T)
sjPlot::plot_model(glmm_wps_PL, show.values = TRUE, width = 0.1, title = "effect of treatment on PL seed number per infructescence")

sjPlot::tab_model(glmm_wps2_PL,show.intercept = T)
sjPlot::plot_model(glmm_wps2_PL, show.values = TRUE, width = 0.1, title = "effect of transplantation on PL seeds number per infructescence") 

sjPlot::tab_model(glmm_wps3_PL,show.intercept = T)
plot_model(glmm_wps3_PL, show.values = TRUE, width = 0.1, title = "effect of warming on PL seeds number per infructescence") 

sjPlot::tab_model(glmm_wps4_PL,show.intercept = T)
plot_model(glmm_wps4_PL, show.values = TRUE, width = 0.1, title = "effect of competition on PL seeds number per infructescence") 



summary(glht(glmm_wps_PL, mcp(condi="Tukey")))
```
LM: NS
```{r}
glmm_wps1_LM<- lmer(log(weight.seed.log)~condi + (1|blockID), data=df[df$species=="LM",])



glmm_wps2_LM<- lmer(log(weight.seed.log)~site + (1|blockID), data=df[df$species=="LM",])

glmm_wps3_LM<- lmer(log(weight.seed.log)~temp +  (1|blockID), data=df[df$species=="LM",])


glmm_wps4_LM<- lmer(log(weight.seed.log)~treat2 +  (1|blockID), data=df[df$species=="LM",])

sjPlot::tab_model(glmm_wps1_LM,show.intercept = T)
sjPlot::plot_model(glmm_wps1_LM, show.values = TRUE, width = 0.1, title = "effect of treatment on LM seed number per infructescence")

sjPlot::tab_model(glmm_wps2_LM,show.intercept = T)
sjPlot::plot_model(glmm_wps2_LM, show.values = TRUE, width = 0.1, title = "effect of transplantation on LM seeds number per infructescence") 

sjPlot::tab_model(glmm_wps3_LM,show.intercept = T)
plot_model(glmm_wps3_LM, show.values = TRUE, width = 0.1, title = "effect of warming on LM seeds number per infructescence") 

sjPlot::tab_model(glmm_wps4_LM,show.intercept = T)
plot_model(glmm_wps4_LM, show.values = TRUE, width = 0.1, title = "effect of competition on LM seeds number per infructescence") 
```

no interactions

Community Weighted Mean CWM
library(FD)

df_TP <- df_TP %>% 
  mutate(
    flowers = replace(flowers, "NULL", NA)
  )
df %>% 
  drop_na(var2)

res.aov <- jobsatisfaction %>% anova_test(score ~ gender * education_level)
res.aov
qqq plot :

qqnorm(scale(body_mass))
abline(a=0, b=1, col = "red")



ggplot(df, aes(x_var, y_var)) +
  geom_point() +
  facet_wrap(vars(category_var))

ggplot(data_air_nona, aes(x = Month, y = Ozone))

box_plot +
    geom_boxplot() +
    geom_dotplot(binaxis = 'y',
        dotsize = 1,
        stackdir = 'center') +
    theme_classic()

ggplot(data=df2, aes(x=dose, y=len, fill=supp)) +
  geom_bar(stat="identity")


facet grid

